XX

### 2019-05-26 paper/manuscript.Rmd
Add references for data sources of web of life

---
title: "XX"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
# bibliography: phd-bibliography/pollen-competition.bib
csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

@@

```{r}
loadd(config)
loadd(int_metadata)
n_published_studies <- int_metadata$reference %>%
  unique() %>%
  stringr::str_detect(pattern = "unpubl", negate = TRUE) %>%
  sum()
```

@@

>>>>

---
title: "XX"
author: 
  - "E. Fernando Cagua^1^ ([efc29@uclive.ac.nz](mailto:efc29@uclive.ac.nz))"
  - "Audrey Lustig^2^ ([audrey.lustig@canterbury.ac.nz](audrey.lustig@canterbury.ac.nz))"
  - "Jason M. Tylianakis^1^ ([jason.tylianakis@canterbury.ac.nz](jason.tylianakis@canterbury.ac.nz))"
  - "Daniel B. Stouffer^1^ ([daniel.stouffer@canterbury.ac.nz](daniel.stouffer@canterbury.ac.nz))"
bibliography: 
  - bibliography.bib
  - int-bibliography.bib
# csl: ecology-letters.csl
output: #word_document
  bookdown::pdf_document2:
    # base_format: rticles::peerj_article
    keep_tex: yes
    number_sections: false
toc: false
fontsize: 11pt
# classoption: a4paper
geometry: 
  - textwidth=33em
  - textheight=48\baselineskip
header-includes:
  - \usepackage{booktabs}
  - \usepackage{setspace}
  - \usepackage{lineno}
  - \usepackage{xr}
  - \usepackage[utf8]{inputenc}
  - \newcommand{\R}[1]{\label{#1}\linelabel{#1}}
  - \newcommand{\lr}[1]{page~\pageref{#1}, line~\lineref{#1}}
  - \externaldocument[S-]{supp-info}
  - \usepackage[export]{adjustbox}
---

@@

```{r}
loadd(config)
loadd(int_metadata)
loadd(interaction_citations)

n_published_studies <- int_metadata$reference %>%
  unique() %>%
  stringr::str_detect(pattern = "unpubl", negate = TRUE) %>%
  sum()

all_int_cites <- paste0("@", interaction_citations$BIBTEXKEY) %>%
  glue::glue_collapse(sep = "; ") %>%
  paste0("[", ., "]")
```

@@

Studies are `r all_int_cites`
